How to Name a Real-World Object, and how not to

### 2019-12-06 papers/ACL2020/manynames.tex
basic analysis for entry-level names in sec 3.3

\paragraph{Of ManyNames:} 
\cs{+ @sz?}\\
\cs{Here goes what has not been discussed in LREC paper, because it focusses on entry-level names. }
\cs{Results aimed to show that we need \underline{multiple} annotations per object \underline{instance} to get the entry-level name}
\begin{itemize}
	\item Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level) \gbt{But, what's an object class in our data? We can't really use collection synsets, can we? Those are not really object classes?} \gbt{UPDATE: We change focus from class to ``entry-level names are instance-specific''. Matthijs is on it.}
	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs. 1 vs. 2 vs. 3). (i.e.,\ entry-level names cannot be derived from a few annotators). \gbt{UPDATE:}
          \begin{itemize}
          \item The average change in most frequent name across rounds is 20\% (SD 2.4\%) -- i.e. even having 9 names only assures you to get the entry-level name for 80\% of the objects on average. \gbt{The data would be more compelling if we did proper sampling (samples of 1, 2, 3, ... names). Matthijs is on it. }
          \end{itemize}
	\item Coverage of set of topN MN names (MN442) wrt all VG objects \cs{@\sz} \gbt{According to my data, there are 415 entry-level names (=entry-level names for canonical object; could extend definition to all objects if need be). Are your 442 names the most frequent names for some image? Else, we could do the experiments with the entry-level names as the vocabulary (but it's probably too late now).}
	\item ...
\end{itemize}

>>>>

\cs{+ @sz?}\\
\cs{Here goes what has not been discussed in LREC paper, because it focusses on entry-level names. }
\cs{Results aimed to show that we need \underline{multiple} annotations per object \underline{instance} to get the entry-level name}

\paragraph{Definition of ``Entry-level Name''} \sz{has this been mentioned before?} In the following, we consider a name annotated for an object as an entry-level name if it corresponds to the most frequent name given a set of name annotations for an object.

\paragraph{Entry-level Names in ManyNames:} As shown in Table \ref{tab:stat-entry-level}, ManyNames provides a large vocabulary of names (7970) for 25K objects. Note that this vocabulary is much larger than what state-of-the-art object detectors are typically trained on. The vocabulary of entry-level names is drastically smaller and contains only 442 types. This small set, however, covers at least 50\% of the objects in VisualGenome, i.e. almost 2M objects in VisualGenome are mentioned in a region descriptions with one of these 442 entry-level names.

\begin{figure}
	\centering
	\small
	\begin{tabular}{p{3cm}p{3cm}}
%VisualGenome+ManyNames & \cite{snodgrass}\\
\centering
\includegraphics[scale=0.15]{images/2327551_2960743_seed_ambiguous.png} &
\includegraphics[scale=0.15]{images/2358126_805887_singleton_obj.png}\\
 bird\ (27),  duck\ (8) & duck (33), bird (3)\\
\end{tabular}

	\caption{Different naming preferences for different instances of the same class (duck)\label{fig:duck}}
\end{figure}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{p{5cm}l}
		\toprule		
\# objects in MN & 25,315\\
total vocab  &  7,970\\
entry-level vocab & 442\\
\# objects with entry-level name in VG & $\sim$ 2M (50\%)\\
\midrule
av. agreement all names & 34.9\%\\
av. agreement entry-level names & 75.2\%\\
av. agreement entry-level cluster & 42.3\%\\
\midrule
av. adequacy all names & 0.81\\
av. adequacy entry-level names & 0.97 \\
av. adequacy entry-level cluster & 0.94 \\
\bottomrule	
	\end{tabular}
	\caption{Basic statistics for entry-level names in MN}
	\label{tab:stat-entry-level}
\end{table}

\paragraph{Entry-level Names are Instance-Dependent:} In a traditional, taxonomic view of object naming, entry-level names can be determined solely based on the object's class, meaning that all instances of a class have the same entry-level name. The MN data provides evidence that this is not the case, even though we do not have access to ground-truth class annotations in \vg (we only have names). Instead, we observe that there are many pairs of entry-level names that do not have a fixed preference ordering across instances, as illustrated in Figure \ref{fig:duck} where the rather non-prototypical instance of a \textit{duck} is named \textit{bird} by most annotators. We find that there are 879 pairs of entry-level names that show a different preference ordering depending on the instance (e.g. \textit{boy-player}, \textit{sandwich-food}, \textit{building-church}, ...).
\sz{does this solve this? Statistics wrt entry-level of object class != entry-level of its instances to (i.e.,\ entry-levels cannot be derived on class-level)} \gbt{But, what's an object class in our data? We can't really use collection synsets, can we? Those are not really object classes?} \gbt{UPDATE: We change focus from class to ``entry-level names are instance-specific''. Matthijs is on it.}

\begin{itemize}
	\item Plot of how most frequent name changes in relation to the number of responses collected (e.g., phase 0 vs. 1 vs. 2 vs. 3). (i.e.,\ entry-level names cannot be derived from a few annotators). \gbt{UPDATE:}
          \begin{itemize}
          \item The average change in most frequent name across rounds is 20\% (SD 2.4\%) -- i.e. even having 9 names only assures you to get the entry-level name for 80\% of the objects on average. \gbt{The data would be more compelling if we did proper sampling (samples of 1, 2, 3, ... names). Matthijs is on it. }
          \end{itemize}

\end{itemize}
